---
title: "expr_analysis"
author: "Joshua Ashkinaze"
date: "2023-07-06"
output: html_document
---

# Load Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(emmeans)
library(dplyr)
library(plm)
library(sandwich)
library(stringr)
library(jtools)
library(readr)
library(sandwich)
library(stargazer)
library(lubridate)
library(ggthemes)
library(lme4)
library(rjson)
library(forcats)
library(ggplot2)
library(readr)
library(dplyr)
library(tidyverse)


emm_options(lmerTest.limit = 17000)
emm_options(pbkrtest.limit = 17000)
knitr::opts_chunk$set(echo = TRUE)

# @TODO: Make sure Python graphs use same color scheme 
hex_color_list = c(
    "#826AED",  # Medium slate blue
    "#00A896",  # Persian green
    "#D41876",  # Telemagenta
    "#020887",  # Pale azure
    "#F7B2AD",  # Melon
    "#342E37",  # Dark grayish-purple
    "#7DCD85",  # Emerald
    "#E87461",  # Medium-bright orange
    "#E3B505",  # Saffron
    "#2C3531",  # Dark charcoal gray with a green undertone
    "#D4B2D8",  # Pink lavender
    "#7E6551",  # Coyote
    "#F45B69",  # Vibrant pinkish-red
    "#020887",   # Phhtalo Blue,
    "#F18805"  # Tangerine

)


# UTILITY FUNCTIONS

relabel_func <- function(x) {
  x %>% 
    str_replace_all("_", " ") %>%
    tools::toTitleCase()
}

create_bins_labels <- function(df, num_bins, variables) {
  breaks = seq(0, 100, by = 100 / num_bins)
  short_labels = paste0("Q", 1:num_bins)
  long_labels = paste0("Q", 1:num_bins, "\n(", breaks[-length(breaks)], "-", as.integer(breaks[-1]), " Percentile)")
  for (var in variables) {
    df[[paste0(var, "_binned")]] <-
      cut(
        df[[var]],
        breaks = breaks,
        labels = short_labels,
        include.lowest = TRUE
      )
    df[[paste0(var, "_binned_long")]] <-
      cut(
        df[[var]],
        breaks = breaks,
        labels = long_labels,
        include.lowest = TRUE
      )
  }
  return(df)
}


# Human-AI copying
```

# Set Up Data

```{r get_data}

# Set birthday
set.seed(416)

# Read the CSV files
expr_data <- read_csv("../../data/experiment_data/experiment_aut_scores.csv")
elab_and_div_scores <- read_csv("../../data/experiment_data/data_clean_with_elab_div_metrics.csv")

# Merge the DataFrames on the response_id column
# Earlier logic (`get_data.ipynb`) describes the logic for who to exclude from analysis. # For context, it's ~30 responses.
df <- merge(expr_data, elab_and_div_scores, by = "response_id", all.x = TRUE)
df <- df %>%
  filter(exclude_from_analysis == 0)# Display the merged DataFrame
print(df)

# Interest group indexes the category in which the source came from
df <- df %>%
  mutate(interest_group = case_when(
    source %in% c('Creative Mornings newsletter', 'r/writing', 'r/poetry') ~ "creative",
    source %in% c('r/artificial', 'r/chatgpt', 'r/InternetIsBeautiful', 'r/singularity') ~ "technology",
    source %in% c('share', 'facebook', 'r/samplesize', 'other') ~ 'neutral',
    TRUE ~ "error"
  ))
df$interest_group <- relevel(factor(df$interest_group), ref = "neutral")


# Fix duration with log(duration) --> squashes extreme values
df <- df %>% mutate(log_duration = log(duration))

# Make condition a factor 
df$condition <- as.factor(df$condition)
df$condition <- factor(df$condition, levels=c('h', 'f_l', 'f_u', 'm_l', 'm_u'))
df$condition <- relevel(df$condition, ref = "h")


# Add columns that break condition into transparency and exposed
df <- df %>%
  mutate(exposure = case_when(
    condition %in% c('h') ~ 'Control',
    condition %in% c('m_l', 'm_u') ~ 'Hi',
    condition %in% c('f_l', 'f_u', 'h') ~ 'Low',
  ),
  transparency = case_when(
    condition %in% c('h') ~ 'Control',
    condition %in% c('m_l', 'f_l') ~ 'Labeled',
    condition %in% c('m_u', 'f_u') ~ 'Unlabeled',
  ))
df$exposure <- relevel(factor(df$exposure), ref = "Control")
df$transparency <- relevel(factor(df$transparency), ref = "Unlabeled")

# Recode with celan names
df <- df %>% mutate(condition = recode(condition,
  "h" = "Control", 
  "f_l" = "Lo_Label", 
  "f_u" = "Lo_Unlabel",
  "m_l" = "Hi_Label", 
  "m_u" = "Hi_Unlabel"
))

# Create a `response_chain_id` which is the block a participant submitted a
# particular trial in
df$response_chain_no <- df$response_chain
df$response_chain_id <- paste(df$response_chain_no, df$condition, df$item)
df$item_condition <-  paste(df$condition, df$item)
df <- df %>%
  mutate(ai_feeling = ifelse(ai_feeling == "", NA, ai_feeling))

# Relevel ai_feeling so neutral is baseline
# Label condition as a factor
df$ai_feeling <- as.factor(df$ai_feeling)
df$ai_feeling <- factor(df$ai_feeling, levels=c('concerned', 'neutral', 'excited'))
df$ai_feeling <- relevel(df$ai_feeling, ref = 'neutral')

variables = c("creativity_ai", "creativity_human")
df <- create_bins_labels(df, 4, variables)

df$creativity_ai_ebinned <- cut(df$creativity_ai, 4)
df$creativity_human_ebinned <- cut(df$creativity_human, 4)

# Multiply dist_cent by 100 for interpretation
df$cent_dist2 <- df$cent_dist*100
df$ai_max_sim2 <- df$ai_max_sim*100

# Create indicator variable for creativity_ai > human
df$create_gap <- df$creativity_ai-df$creativity_human
df$create_gap_cut <- as.integer((df$creativity_ai > df$creativity_human)*1)
```

# Fit Models

```{r fit_models}
library(lme4)
library(combinat)

# Define the grid search function
grid_search_interaction <- function(dv, df, variables) {
  # Base model formula
  base_formula <- as.formula(
    paste(
      dv,
      "~ condition +
                creativity_human_binned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                creativity_ai_binned + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)"
    )
  )
  
  # Generate the power set of interactions
  all_combinations <- list()
  for (i in 1:length(variables)) {
    all_combinations <-
      append(all_combinations, combn(variables, i, simplify = FALSE))
  }
  all_combinations <- unlist(all_combinations, recursive = FALSE)
  interaction_combinations <-
    lapply(all_combinations, function(combo) {
      paste(paste(combo, "condition", sep = ":"), collapse = " + ")
    })
  
  # Fit the base model once. Then init lists for BIC and models 
  base_model <- lmer(base_formula, data = df)
  base_bic <- BIC(base_model)
  models <- list(base_model)
  bics <- c(base_bic)
  
  # Grid search over interactions
  for (i in seq_along(interaction_combinations)) {
      formula_i <- update(base_formula, paste(". ~ . +", interaction_combinations[[i]]))
      models[[i+1]] <- lmer(formula_i, data = df) # i+1 since we already have the base model
      bics[i+1] <- BIC(models[[i+1]])
  }
  best_model_index <- which.min(bics)
  best_model <- models[[best_model_index]]
  print(paste("Selected model with lowest BIC:", 
              ifelse(best_model_index == 1, "Base model", interaction_combinations[[best_model_index - 1]])))
  print(summary(best_model))
  return(best_model)
}

models <- list()
possible_interactions <- c("interest_group", "create_gap", "creativity_ai_binned")
dvs <- c('cent_dist2', 'elab_ibf', 'originality', 'ai_max_sim2')

for (dv in dvs) {
  models[[dv]] <-
    grid_search_interaction(dv, df, possible_interactions)
}

names(models) <-
 c("Diversity", "Elaboration", "Originality", "AI Adoption")

```

# Save emmeans

So the basic issue is that it takes a long time to fit emmeans reference
grids with crossed random intercepts and I need a bunch of them. To save
time, I will get the models now.

```{r save_emmeans}

model_names <- as.character(names(models))

# Functions to get stuff from models
#####################################
#####################################

# Function to get interactions from the model
get_interactions <- function(model_name) {
  model <- models[[model_name]]
  model_terms <- attr(terms(model), "term.labels")
  vars_of_interest <-
    c("ai_feeling", "creativity_human_binned", "creativity_ai_binned", "interest_group", "trial_no", "gap")
  interactions <-
    model_terms[str_detect(model_terms, "condition") &
                  str_detect(model_terms, paste(vars_of_interest, collapse = "|"))]
  interactions <- str_remove(interactions, "condition:")
  return(interactions)
}

# Function to get emmeans from the model
get_emmeans <- function(model_name) {
  model <- models[[model_name]]
  interactions <-
    c(interaction_list[[model_name]],
      "creativity_human_binned + creativity_ai_binned")
  emmeans_results <- list()
  emmeans_results['overall'] = emmeans(model, specs = ~ condition)
  for (interaction in interactions) {
    if (interaction != "trial_no") {
      em_formula <- as.formula(paste0("~ condition*", interaction))
      em.temp <- emmeans::emmeans(model, specs = em_formula)
    } else {
      em.temp <-
        emmeans::emtrends(model,
                          ~ condition |
                            trial_no,
                          var = "trial_no",
                          )
    }
    emmeans_results[[interaction]] = em.temp
  }
  return(emmeans_results)
}
#####################################
#####################################
#~ machine | diameter, var = "sqrt(diameter)", 
        # at = list(diameter = c(20, 30))
# Get stuff from models if didn't get yet
#####################################
#####################################
if (!file.exists("models.rds")) {
  
  interaction_list <- list()
  emmeans_list <- list()
  joint_tests_list <- list() 
  
  for (model_name in model_names) {
    interaction_list[[model_name]] <- get_interactions(model_name)
     emmeans_list[[model_name]] <- get_emmeans(model_name)
    joint_tests_list[[model_name]] <-  joint_tests(models[[model_name]], rg.limit=30000)
  }
  
  saveRDS(models, "models.rds")
  saveRDS(emmeans_list, "emmeans_list.rds")
  saveRDS(interaction_list, "interaction_list.rds")
  saveRDS(joint_tests_list, "joint_tests.rds")
} else{
  models <- readRDS("models.rds")
  emmeans_list <- readRDS("emmeans_list.rds")
  interaction_list <- readRDS("interaction_list.rds")
  joint_tests <- readRDS("joint_tests.rds")

}
#####################################
#####################################
```

# Core Functions

## Make overall plot

```{r create_plot}
create_plot <- function(model_name) {
  custom_colors <-
    c(
      "Control (None)" = "black",
      "Low" = "#826AED",
      "High" = "#D41876"
    )
  condition_labels <- c(
    "Control" = "Human\nControl",
    "Hi_Label" = "Hi Exposure\n(Labeled)",
    "Lo_Label" = "Lo Exposure\n(Labeled)",
    "Hi_Unlabel" = "Hi Exposure\n(Unlabeled)",
    "Lo_Unlabel" = "Lo Exposure\n(Unlabeled)"
  )
  
  # Get emmeans and CIs
  #####################################
  em <- emmeans(emmeans_list[[model_name]]$overall, ~condition)
  em_df <- em %>% as.data.frame(.) %>% tidy(.)
  conf_df <- confint(em, adjust='none')
  combined_df <-cbind(em_df,
          lower = conf_df$lower.CL,
          upper = conf_df$upper.CL)
  #####################################
  
  
  # Do some data wrangling 
  #####################################
  combined_df <- combined_df %>%
    mutate(
      clean_label = condition_labels[match(condition, names(condition_labels))],
      exposure = ifelse(grepl("Lo_", condition), "Low",
                        ifelse(grepl("Hi_", condition), "High", "Control (None)")),
      transparency = ifelse(
        grepl("Label", condition),
        "Labeled",
        ifelse(grepl("Unlabel", condition), "Unlabeled", "Control")
      )
    )
    #####################################
  
  
  # Make plot
  #####################################
  p <-
    ggplot(combined_df,
           aes(
             x = reorder(clean_label, estimate),
             y = estimate,
             color = exposure,
             shape = transparency
           )) +
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
    labs(x = "Condition", y = model_name) +  # Use the model name as the y-axis label
    scale_color_manual(values = custom_colors) +
    theme_nice(base_family = 'Arial') +
    labs(
      title = paste("How AI Exposure and Transparency Affect", model_name),
      subtitle = "Estimated marginal means and 95% CIs from mixed model."
    )
  ggsave(paste0(model_name, "_overall.png"), dpi=300)
  
  return(p)
  #####################################
}
```

## Overall FX

```{r overall_fx}
overall_fx <- function(model_name) {
  
  set.seed(123)
  if (model_name != 'AI Adoption') {
    con <- list(
      "AI - Human" = c(-0.5, 0.125, 0.125, 0.125, 0.125),
      "Hi Exposure - Low Exposure" = c(0, -0.25, -0.25, 0.25, 0.25),
      "Labeled - Unlabeled" = c(0, 0.25, -0.25, 0.25, -0.25)
    )
  }
  # f_l, f_u, m_l, m_u
  else {
      con <- list(
      "Hi Exposure - Low Exposure" = c(-0.25, -0.25, 0.25, 0.25),
      "Labeled - Unlabeled" = c(0.25, -0.25, 0.25, -0.25)
    )
  }
  
  adj = 'holm'
  
  model <- models[[model_name]]
  em.original <- emmeans_list[[model_name]]$overall
  print(contrast(em.original, adj=adj))
  
  em.f_test <- joint_tests[[model_name]]
  print(em.f_test)
  
  em.contrast <- emmeans(em.original, ~condition, contr=con, adj=adj)
  print(em.contrast$contrasts)
  
  em.pw <- emmeans(em.original, ~condition, adj=adj)
  print(pairs(em.pw), adj=adj)
  
}
```

# Adoption

## Overall Effects

1.  There are no overall effects on adoption, though by construction hi
    exposure has more adoption than low exposure.

```{r}
overall_fx("AI Adoption")
create_plot("AI Adoption")
```

## Group Differences

Adoption does differ by condition X creativity (F(9, 1949.71) = 3.317)
and interest group (F(2, 545.79)= 3.209).

```{r}
overall_fx("AI Adoption")

```

### Creativity

```{r}

mean_value <- mean(df$ai_max_sim2, na.rm=TRUE)


edf <-
  emmeans(emmeans_list$`AI Adoption`$creativity_human_binned,
           by = 'creativity_human_binned', ~condition*creativity_human_binned,
           adj = 'none') %>%
  as.data.frame(.) %>%
  tibble(.) %>%
  filter(condition %in% c("Hi_Label", "Hi_Unlabel")) %>%
  mutate(condition = recode(condition,
                           "Hi_Label" = "High Exposure (Labeled)",
                           "Hi_Unlabel" = "High Exposure (Unlabeled)"))

ggplot(data=edf, aes(x=creativity_human_binned, y=emmean)) +
  labs(title="The relationship between AI transparency and AI idea adoption\nby creativity", 
       subtitle="Marginal means +- SE by creativity quartile; dashed line for overall mean",
       x="Creativity Quartile",
       y="Estimated Marginal Mean of AI Adoption ") +
  scale_color_brewer(palette = "Paired", direction=-1) + 
geom_hline(aes(yintercept=mean_value), color="black", linetype="dashed", size=1) +
  geom_point(size = 5, position=position_dodge(0)) +
  facet_wrap(~condition) + 
  geom_line(aes(group=creativity_human_binned), size=1) +
    geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), width=0.5, position=position_dodge(0.5), alpha=0.4) +


  theme_nice(base_family='Arial')
```

### Interactions: Contrast of contrasts or contrast of EMMs?

```{r calc-interactions}

ema <- emmeans(emmeans_list$`AI Adoption`$creativity_human_binned,  by='creativity_human_binned', ~condition)

# # Contrast of contrasts
# em2 <- contrast(emmeans_list$`AI Adoption`$creativity_human_binned,  by='creativity_human_binned', adjust='holm')
# em3 <- pairs(em2, simple='creativity_human_binned', adjust='holm')
# print(em3)

```

```{r pretty-plots}
library(RColorBrewer)


# AI ADOPTION: Snaking Lines
############################
mean_value <- mean(df$ai_max_sim2, na.rm=TRUE)
edf <-
  emmeans(emmeans_list$`AI Adoption`$creativity_human_binned,
           by = 'creativity_human_binned', ~condition*creativity_human_binned,
           adj = 'none') %>%
  as.data.frame(.) %>%
  tibble(.) %>%
  filter(condition %in% c("Hi_Label")) %>%
  mutate(condition = recode(condition,
                           "Hi_Label" = "High Exposure (Labeled)",
                           "Hi_Unlabel" = "High Exposure (Unlabeled)"))

ggplot(data=edf, aes(x=creativity_human_binned, y=emmean)) +
  labs(title="How self-percieved creativity moderates the effect of AI transparency\non idea adoption in the (High Exposure, Labeled) condition", 
       subtitle="Marginal means +- SE; dashed line for overall mean",
       x="Self-Percieved Human Creativity",
       y="Estimated Marginal Mean of AI Adoption ") +
geom_hline(aes(yintercept=mean_value), color="black", linetype="dashed", size=1) +
  geom_point(size = 5, position=position_dodge(0)) +
  geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), width=0.5, position=position_dodge(0.5), alpha=1) +
  geom_line(aes(group=condition), size=1) +

  theme_nice(base_family='Arial')
############################



# AI ADOPTION: Crossed Lines
############################
mean_value <- mean(df$ai_max_sim2, na.rm=TRUE)
edf <-
  emmeans(emmeans_list$`AI Adoption`$creativity_human_binned,
           by = 'creativity_human_binned', ~condition*creativity_human_binned,
           adj = 'none') %>%
  as.data.frame(.) %>%
  tibble(.) %>%
  filter(condition %in% c("Hi_Label", "Hi_Unlabel")) %>%
  mutate(condition = recode(condition,
                           "Hi_Label" = "High Exposure (Labeled)",
                           "Hi_Unlabel" = "High Exposure (Unlabeled)"))

ggplot(data=edf, aes(x=condition, y=emmean, colour=creativity_human_binned)) +
  labs(title="How self-percieved creativity moderates the effect of AI transparency\non idea adoption", 
       subtitle="Marginal means by creativity quartile; dashed line for overall mean",
       x="Condition",
       y="Estimated Marginal Mean of AI Adoption ") +
  scale_color_brewer(palette = "RdBu") + 
geom_hline(aes(yintercept=mean_value), color="black", linetype="dashed", size=1) +
  geom_point(size = 5, position=position_dodge(0)) +
  geom_line(aes(group=creativity_human_binned), size=1) +
    theme_nice(base_family='Arial')

############################




```

### Show this replicates within interest groups

```{r}
overall_mean <- mean(df$ai_max_sim2, na.rm=TRUE)
df %>% 
  group_by(interest_group, transparency) %>%
  summarise(m = mean(ai_max_sim2, na.rm = TRUE), 
            sd = sd(ai_max_sim2, na.rm = TRUE), 
            n = n(), 
            se = sd / sqrt(n)) %>%
  na.omit() %>%
  ggplot(aes(x = interest_group, y = m)) + 
  geom_point(size = 5) + 
  facet_wrap(~transparency) + 
  theme_nice(base_family='Arial') + 
  geom_errorbar(aes(ymin = m - se, ymax = m + se)) + 
  labs(x="Interest Group", y="Mean AI Adoption", title="AI Adoption by Interest Group", subtitle = "Mean +- SE of AI Adoption by interest group where 'interest group' describes\n the source of participants. The horizontal line is overall mean.") + 
  geom_hline(aes(yintercept=overall_mean), color="black", linetype="dashed", size=1) 




```

### Adoption items

Show that people are most influenced by AI for the hardest tasks

#### Mixed model method gives identical results to raw data!!

```{r}

lm.item <-  
  lmer(originality ~ item +  ai_feeling + creativity_human_binned*condition + creativity_ai_binned*condition + ai_feeling*condition + interest_group + condition_order +  
    trial_no + log_duration + item*condition + (1|response_chain_id) + (1|participant_id), data = df) %>% 
  emmeans(., ~item|condition) %>% 
  as.data.frame(.) %>% tibble(.) %>% 
  filter(condition %in% c("Control")) %>% 
  mutate(orig = -1 * emmean) %>% 
  mutate(rank_orig = rank(orig))

lm.adopt_both <- lmer(ai_max_sim ~ condition + item + condition*item + creativity_human_binned*condition + creativity_ai_binned*condition + ai_feeling*condition + interest_group + condition_order + trial_no + log_duration +(1|response_chain_id) + (1|participant_id), data=df) %>%
  emmeans(., ~item|condition) %>%
  as.data.frame(.) %>% tibble(.) %>%
  filter(condition %in% c("Hi_Label", "Hi_Unlabel"))

lm.adopt_label <- lm.adopt_both %>% 
  filter(condition == "Hi_Label") %>%
  mutate(rank_Hi_Label = rank(emmean)) %>%
  select(item, emmean_Hi_Label = emmean, rank_Hi_Label)

lm.adopt_unlabel <- lm.adopt_both %>% 
  filter(condition == "Hi_Unlabel") %>%
  mutate(rank_Hi_Unlabel = rank(emmean)) %>%
  select(item, emmean_Hi_Unlabel = emmean, rank_Hi_Unlabel)

lm.adopt_wide <- left_join(lm.adopt_label, lm.adopt_unlabel, by = "item")
#########################

# Get correlation  
#########################
items_df <- inner_join(lm.adopt_wide, lm.item, by="item")
correlation <- stats::cor(items_df$emmean_Hi_Label, items_df$orig, method="spearman")
correlation.unlabel <- stats::cor(items_df$emmean_Hi_Unlabel, items_df$orig, method="spearman")

print("Correlation for labeled")
print(correlation)

print("Correlation for unlabeled")
print(correlation.unlabel)
#########################

# Make graph 
#########################
cor_plot <- ggplot(items_df, aes(x = rank_orig, y = rank_Hi_Label)) +
  geom_point(aes(color = item), size = 8) + 
  scale_color_discrete(guide = guide_legend(override.aes = list(size = 6))) + 
  geom_smooth(method = "lm", size=2, se = FALSE, color = "black") +  # Add a simple straight line

  annotate("text", x = max(items_df$rank_orig), y = min(items_df$rank_Hi_Label), 
           label = paste("Spearman rho =", round(correlation, 2)), vjust=-3, hjust = 1) +  
  labs(
    title = "Adoption of AI Ideas by Difficulty of AUT Prompt",
    subtitle = "Prompt difficulty for an item was measured by the inverse rank of average originality\nin the control condition (i.e: lower average originality suggests a more difficult prompt).\n\nAdoption was measued by the rank of cosine similarity of participant responses\nto AI examples in the (High Exposure, Labeled) condition.",
    x = "Rank of Difficulty of Prompt (1-5)",
    y = "Rank of AI Adoption (1-5)",
    color = "Item"
  ) + 
  theme_nice(base_family='Arial') +
  scale_color_manual(values = hex_color_list, guide = guide_legend(override.aes = list(size = 10)))
cor_plot
ggsave("cor_adopt.png", dpi=400)
```

#### Raw data

```{r}

df.originality <- df %>% 
  filter(condition %in% c("Control")) %>% 
  group_by(item) %>% 
  summarise(m = mean(originality)) %>% 
  ungroup() %>%
  mutate(rank_orig = rank(m))

df.adoption.unlabel <- df %>% 
  filter(condition %in% c("Hi_Unlabel")) %>% 
  group_by(item, condition) %>% 
  summarise(m = -1*mean(ai_max_sim)) %>% 
  ungroup() %>% 
  mutate(rank_unlabel = rank(m))

df.adoption.label <- df %>% 
  filter(condition %in% c("Hi_Label")) %>% 
  group_by(item, condition) %>% 
  summarise(m = -1*mean(ai_max_sim)) %>% 
  ungroup () %>% 
  mutate(rank_label = rank(m))  

merged_df <- df.originality %>% 
  left_join(df.adoption.unlabel, by = "item") %>%
  left_join(df.adoption.label, by = "item")


# Get Correlations
#########################
correlation <- stats::cor(merged_df$rank_orig, merged_df$rank_label, method="spearman")
correlation.unlabel <- stats::cor(merged_df$rank_orig, merged_df$rank_unlabel, method="spearman")

print("Correlation for labeled")
print(correlation)

print("Correlation for unlabeled")
print(correlation.unlabel)
#########################



# Make graph 
#########################
cor_plot <- ggplot(merged_df, aes(x = rank_orig, y = rank_label)) +
  geom_point(aes(color = item), size = 8) + 
  scale_color_discrete(guide = guide_legend(override.aes = list(size = 6))) + 
  geom_smooth(method = "lm", size=2, se = FALSE, color = "black") +  # Add a simple straight line

  annotate("text", x = max(merged_df$rank_orig), y = min(merged_df$rank_label), 
           label = paste("Spearman rho =", round(correlation, 2)), vjust=-3, hjust = 1) +  
  labs(
    title = "Adoption of AI Ideas by Difficulty of AUT Prompt",
    subtitle = "Prompt difficulty for an item was measured by the inverse rank of average originality\nin the control condition (i.e: lower average originality suggests a more difficult prompt).\n\nAdoption was measued by the rank of cosine similarity of participant responses\nto AI examples in the (High Exposure, Labeled) condition.",
    x = "Rank of Difficulty of Prompt (1-5)",
    y = "Rank of AI Adoption (1-5)",
    color = "Item"
  ) + 
  theme_nice(base_family='Arial') +
  scale_color_manual(values = hex_color_list, guide = guide_legend(override.aes = list(size = 10)))
cor_plot
ggsave("cor_adopt.png", dpi=400)
  
```

```         
```

# Diversity

## Overall fx = null

```{r}
overall_fx("Diversity")
create_plot("Diversity")
```

## Same difference for High Labeled as adoption

```{r}

edf <-
  emmeans(emmeans_list$`Diversity`$creativity_human_binned,
           by = 'creativity_human_binned', ~condition*creativity_human_binned,
           adj = 'none') %>%
  as.data.frame(.) %>%
  tibble(.) %>% filter(condition %in% c('Hi_Label', 'Hi_Unlabel'))

ggplot(data=edf, aes(x=creativity_human_binned, y=emmean)) +
  labs(title="The relationship between AI transparency and AI idea adoption\nby creativity", 
       subtitle="Marginal means +- SE by creativity quartile; dashed line for overall mean",
       x="Creativity Quartile",
       y="Estimated Marginal Mean of AI Adoption ") +
  scale_color_brewer(palette = "Paired", direction=-1) + 
  geom_point(size = 5, position=position_dodge(0)) +
  facet_wrap(~condition) + 
  geom_line(aes(group=creativity_human_binned), size=1) +
    geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), width=0.5, position=position_dodge(0.5), alpha=0.4) +theme_nice(base_family='Arial')
```

## Temporal fx st high exposure lower loss of diversity over time

```{r}
stargazer(models$Diversity, type='text')

df %>% group_by(condition, exposure, transparency, trial_no) %>% filter(trial_no <=20) %>%
  summarise(m = mean(cent_dist2)) %>%
  ggplot(data=., aes(x=trial_no, y=m)) + geom_point() + facet_wrap(~condition) + geom_smooth(method='lm') + theme_nice() + labs(title="Semantic Diversity over Time by Condition", subtitle="Each dot represents the condition-level mean centroid distance for a trial number\nacross all items and response chains") + theme_nice(base_family="Arial")
  
```

```{r}


# # WORD COUNT OVER EXPR TRIALS  
# df %>%
#   filter(trial_no <= 20) %>% filter(trial_no >= 0) %>% 
#   group_by(trial_no, condition) %>%
#   summarise(m = mean(originality, na.rm = TRUE)) %>% 
#   ggplot(aes(x = trial_no, y = m, group = interaction(condition))) +
#   facet_wrap(~ condition, scales = 'fixed') + 
#   theme_nice() + 
#   geom_point() + 
# geom_smooth(method = 'loess', se=TRUE, alpha=0.01)


# WORD COUNT OVER EXPR TRIALS
df %>%
  filter(trial_no <= 20) %>% filter(trial_no >= 0) %>%
  group_by(trial_no, condition) %>%
  summarise(m = mean(originality, na.rm = TRUE)) %>%
  ggplot(aes(x = trial_no, y = m, group = interaction(condition))) +
  facet_wrap(~ condition, scales = 'fixed') +
  theme_nice() +
  geom_point() +
geom_smooth(method = 'lm', se=FALSE, alpha=0.01)

```

# Robustness Checks

## Does creativity finding still hold lookign acrss ai creativity?

```{r}
df %>% 
  group_by(creativity_human_binned, creativity_ai_binned, condition, ai_feeling) %>%
  summarise(m = mean(ai_max_sim2, na.rm = TRUE)) %>%
  na.omit() %>%
  ggplot(data=., aes(x=creativity_human_binned, y=m, colour=creativity_ai_binned, group=interaction(creativity_ai_binned, condition))) + 
  facet_grid(condition ~ ai_feeling) + geom_point(size=3) + 
  theme_nice() 

```

## Creativity Sit

```{r}

quartiles_creativity_ai <- quantile(df$creativity_ai, probs = c(0, 0.25, 0.5, 0.75, 1), na.rm=TRUE)
df$creativity_ai_ebinned <- as.factor(cut(df$creativity_ai, breaks = quartiles_creativity_ai, include.lowest = TRUE, labels = FALSE))

quartiles_creativity_human <- quantile(df$creativity_human, probs = c(0, 0.25, 0.5, 0.75, 1), na.rm=TRUE)
df$creativity_human_ebinned <- as.factor(cut(df$creativity_human, breaks = quartiles_creativity_human, include.lowest = TRUE, labels = FALSE))


base.inter <-   lmer("ai_max_sim2 ~ condition +
                creativity_human_binned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                create_gap + 
                creativity_ai_binned*condition+ 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)


base.simpler <-   lmer("ai_max_sim2 ~ condition +
                creativity_human_binned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                create_gap + 
                creativity_ai_binned + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)

base.cinter <-   lmer("ai_max_sim2 ~ condition +
                creativity_human_ebinned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                create_gap + 
                creativity_ai_ebinned*condition + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)

base <-   lmer("ai_max_sim2 ~ condition +
                creativity_human_ebinned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                create_gap + 
                creativity_ai_ebinned*condition + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)

base.no_inter <-   lmer("ai_max_sim2 ~ condition +
                creativity_human_binned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                create_gap + 
                creativity_ai_binned + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)

eb <- lmer("ai_max_sim2 ~ condition +
                creativity_human_ebinned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                create_gap + 
                condition + 
                creativity_ai_ebinned + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)


stargazer(list(base.inter, base.simpler, base.cinter, base, base.no_inter, eb), type='text', report=('vct*'))
```

```{r}
em %>% as.data.frame(.) %>% tibble(.) %>% 
  filter(condition %in% c('Hi_Label', 'Hi_Unlabel')) %>% 
  ggplot(data=., aes(x=creativity_human_binned, y=emmean, colour=creativity_ai_binned, group=interaction(condition, creativity_ai_binned))) + 
  geom_point() + 
  geom_smooth(method='lm', se=FALSE) + 
  facet_wrap(~condition) 
  theme_nice()
```

```{r}

df$log_creativity_human <- log(df$creativity_human + 1)
df$log_creativity_ai <- log(df$creativity_ai + 1)

base.inter <-   lmer("ai_max_sim2 ~ condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                condition*creativity_human_center + 
                condition*creativity_ai_center + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)


base.inter2 <-   lmer("ai_max_sim2 ~ condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                condition*creativity_human_binned + 
                condition*creativity_ai_binned + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)

stargazer(base.inter, base.inter2, type='text')
```

```{r}
emtrends(base.inter, specs = c("condition"), var = "creativity_human_center", 
          at = list(creativity_human_center = c(5,20)))
```

## Gap analysis

```{r}
df$creativity_ai_centered <- df$creativity_ai - 50
df$creativity_human_centered <- df$creativity_human - 50
ols <- lm(ai_max_sim2 ~ ai_feeling + condition_order + condition*creativity_ai_binned + condition*creativity_human_binned, data=df)
summary(ols)
```

## Trends

```{r}
em <- emtrends(models$Diversity, ~condition*trial_no, var="trial_no", at=list(trial_no=10))
```

```{r}
edf <- em %>% as.data.frame(.) %>% tidy(.)%>% tidyr::crossing(no = 0:20) %>% mutate(est = 20 + no*trial_no.trend) 
ggplot(data=edf, aes(x=no, y=est, colour=condition)) + geom_line() + facet_wrap(~condition)
```

```{r}
df$creativity_ai_center <- df$creativity_ai - 50
df$creativity_human_center <- df$creativity_human - 50
```

```{r}
df %>% group_by(condition, creativity_human_binned, creativity_ai_binned) %>% summarize(m = mean(ai_max_sim2), sizey=n()) %>% na.omit() %>% ggplot(data =
                                                                                                                                          .,
                                                                                                                                        aes(x = creativity_human_binned, y = m, colour = creativity_ai_binned, group=interaction(creativity_ai_binned, condition))) + facet_wrap( ~
                                                                                                                                                                                                                                condition) + geom_point(size = 4) + geom_line()
```

```{r}
df %>% group_by(condition, creativity_human_binned, create_gap_cut) %>% summarize(m = mean(ai_max_sim2), sizey=n()) %>% na.omit() %>% ggplot(data =
                                                                                                                                          .,
                                                                                                                                        aes(x = creativity_human_binned, y = m, colour = create_gap_cut, group=interaction(create_gap_cut, condition))) + facet_wrap( ~
                                                                                                                                                                                                                                condition) + geom_point(size = 4) 
```

```{r}
# Create Gap 

variables = c("creativity_ai", "creativity_human")
df$create_gap_cut <- (df$creativity_ai > df$creativity_human)*1
```

```{r}
em <- emmeans(models$`AI Adoption`, ~condition|creativity_human_binned,weights='cell')

em2 <- emmeans(emmeans_list$`AI Adoption`$creativity_human_binned, ~condition|creativity_human_binned)
```

# DEBUGGING

```{r}

df$mean_lcs_sim_neg <- -1*df$mean_lcs_sim

base.inter <-   lmer("mean_lcs_sim_neg ~ condition +
                creativity_human_binned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                condition*create_gap_cut + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)


base.inter2 <-   lmer("cent_dist2 ~ condition +
                creativity_human_binned*condition +
                ai_feeling*condition +
                interest_group +
                condition_order +
                trial_no*condition +
                log_duration +
                condition*create_gap_cut + 
                (1|participant_id) +
                (1|item_condition/response_chain_id)", data=df)

stargazer(base.inter,base.inter2, type='text')
```

```{r}
# df$create_gap_cut <- as.integer((df$creativity_ai >= df$creativity_human)*1)
a <- emmeans(base.inter, ~condition*creativity_human_binned)
```

```{r}

a %>% 
  as.data.frame() %>% 
  filter(condition %in% c("Hi_Label", "Hi_Unlabel")) %>% ggplot(data = ., 
            aes(x = creativity_human_binned,
                y = emmean,
                group = interaction(condition, creativity_human_binned))) +
  geom_point(size = 5) + 
  geom_smooth(method = 'lm') +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE)) +
  geom_smooth(method='lm') + 

  facet_wrap(~ condition) +
  geom_hline(yintercept = overall_mean) +
  theme_nice() # Assuming theme_nice is a custom or predefined theme function


```

```{r}

var <- sym('mean_lcs_dist_norm')

df %>%
  group_by(creativity_human_binned, condition, create_gap_cut) %>%
  summarise(m = mean(!!var),
            se = sd(!!var) / sqrt(n()),
            .groups = "drop") %>% # This drops the grouping 
  na.omit() %>%
  ggplot(data = ., aes(x = creativity_human_binned, y = m)) +
  facet_grid(condition~creativity_ai_binned) + 
  geom_point(size = 5) + 
  # Assuming theme_nice() is a custom theme you've defined. If not, you may need to replace it.
  theme_nice() + 
  geom_errorbar(aes(ymin =m-se, ymax = m + se))
```

```{r}
divisors <- seq(1, 50, by=1)
optimal_divisor <- divisors[which.max(sapply(divisors, function(d) shapiro.test(exp(-df$mean_lcs_sim/d))$p.value))]

```
